Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-08 paper/main.tex
[issue 2.2, 2.3] add introducing sentence before 2.1; remove figures 1 and 2

% Use colors for revisions
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\newcommand{\added}[1]{\textcolor{blue}{#1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}
\newcommand{\removed}[1]{\textcolor{gray}{#1}}

@@

@@

In the end, we have 17,344 stars and 47,656 galaxies available
for the training and testing processes.
The apparent magnitudes range from $10.7 < r < 23.1$,
and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
\removed{
The $ugriz$ color-color space of the sample is plotted in
Figure~\ref{fig:sdss_color_color}.
}
We randomly split the objects into training, held-out validation,
and blind test sets of size 40,000, 10,000, and 15,000, respectively.
We note that cross-validation is often avoided in deep learning
in favor of hold-out validation,
since cross-validation is computationally expensive.
We also note that we perform a blind test, and the test set is not used in any
way to train or calibrate the algorithms.
The first two panels of Figure~\ref{fig:sdss_mag} show the number of objects
and the fraction of stars in the test set as functions of $r$-band magnitude.
Similarly, Figure~\ref{fig:sdss_g_r} shows the number of objects and the
fraction of stars in the test set as functions of $g-r$ color.
The normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set,
and they are nearly indistinguishable when overlapped.
We do not show the distributions for the training and validation sets in
Figures~\ref{fig:sdss_mag} and \ref{fig:sdss_g_r} to avoid cluttering the
plots.

@@

In the end, we have 8,545 stars and 57,843 galaxies available
for the training and testing processes.
The apparent magnitudes range from $13.9 < r < 25.6$,
and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
\removed{
The $ugriz$ color-color space of the sample is plotted in
Figure~\ref{fig:clens_color_color}.
}
We randomly split the objects into training, held-out validation, and
blind test sets of size 40,000, 10,000, and 13,278, respectively.
Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
of objects in the test set as functions of $i$-band magnitude and $g-r$ color.
We do not show the distributions for the training and validation sets,
since the normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set.

>>>>

% Use strikethrough and colors for revisions
\usepackage[normalem]{ulem}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\newcommand{\added}[1]{\textcolor{red}{#1}}

@@

\added{
To demonstrate the performance of our ConvNet model, we use photometric and
spectroscopic data sets with different characteristics and compositions.
In this section, we briefly describe these data sets and the image pre-processing
steps for retrieving cutout images.
}

@@

In the end, we have 17,344 stars and 47,656 galaxies available
for the training and testing processes.
The apparent magnitudes range from $10.7 < r < 23.1$,
and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
\sout{
The $ugriz$ color-color space of the sample is plotted in
Figure~\ref{fig:sdss_color_color}.
}
We randomly split the objects into training, held-out validation,
and blind test sets of size 40,000, 10,000, and 15,000, respectively.
We note that cross-validation is often avoided in deep learning
in favor of hold-out validation,
since cross-validation is computationally expensive.
We also note that we perform a blind test, and the test set is not used in any
way to train or calibrate the algorithms.
The first two panels of Figure~\ref{fig:sdss_mag} show the number of objects
and the fraction of stars in the test set as functions of $r$-band magnitude.
Similarly, Figure~\ref{fig:sdss_g_r} shows the number of objects and the
fraction of stars in the test set as functions of $g-r$ color.
The normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set,
and they are nearly indistinguishable when overlapped.
We do not show the distributions for the training and validation sets in
Figures~\ref{fig:sdss_mag} and \ref{fig:sdss_g_r} to avoid cluttering the
plots.

@@

In the end, we have 8,545 stars and 57,843 galaxies available
for the training and testing processes.
The apparent magnitudes range from $13.9 < r < 25.6$,
and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
\sout{
The $ugriz$ color-color space of the sample is plotted in
Figure~\ref{fig:clens_color_color}.
}
We randomly split the objects into training, held-out validation, and
blind test sets of size 40,000, 10,000, and 13,278, respectively.
Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
of objects in the test set as functions of $i$-band magnitude and $g-r$ color.
We do not show the distributions for the training and validation sets,
since the normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set.
